An Algorithmic Introduction to Lagrangian Coherent Structures

### 2013-11-12 main.tex
Add graphics of Bickley jet FTLE at various resolutions

>>>>

Figure~\ref{f:Bickley jet FTLE resolutions} shows the FTLE at various resolutions. Visual inspection of these figures indicates that a resolution of $500 \times 199$ is acceptable since increasing the resolution to $1000 \times 398$ does not change the appearance of the FTLE noticeably.

\begin{figure}
\begin{center}
\includegraphics[width=.85\textwidth]{graphics/bickley_jet/ftle_100_39}
\includegraphics[width=.85\textwidth]{graphics/bickley_jet/ftle_250_99}
\includegraphics[width=.85\textwidth]{graphics/bickley_jet/ftle_500_199}
\includegraphics[width=.85\textwidth]{graphics/bickley_jet/ftle_1000_398}
\end{center}
\caption{Bickley jet FTLE at various resolutions.}
\label{f:Bickley jet FTLE resolutions}
\end{figure}
